Revisiting Multi-Domain Machine Translation

### 2020-04-23 2020/coling2020/multidomain.tex
one more comment

The multi-domain training regime is more the norm than the exception for natural language processing \cite{Dredze08online,Finkel09hierarchical}, and the design of multi-domain systems has been proposed for many language processing tasks. We focus here exclusively on MD machine translation, keeping in mind that similar problems and solutions (parameter sharing, instance selection / weighting, adversarial training, etc) may have been studied in other contexts.

@@

Multi-domain translation was already proposed for statistical MT (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}). Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain labels give rise to additional features.

This latter strategy has also been widely used in MNT: the authors of \cite{Kobus17domaincontrol} inject an additional domain feature in their seq2seq model, either in the form of an extra (initial) domain-token or in the form of additional domain-feature associated to each word. These results are reproduced in \cite{Tars18multidomain}, which also considers, as we do, automatically induced domain tags. This technique also helps control the style of MT outputs in \cite{Sennrich16politeness,Niu18multitask}, and to encode the source or target languages in multilingual MT \cite{Firat16multiway,Johnson17google}. Domain control can also be performed on the target side, as in \cite{Chen16guided}, where a vector of topic describing the current document is included as an extra context in the softmax layer of the decoder. Such ideas are further developed in \cite{Chu18multilingual,Pham19generic}, where domain differences and commonalties are encoded in the network architecture: some parameters
are shared across all domains, while others are domain-specific. % (part of the embeddings in \cite{Pham19generic}).

>>>>

The multi-domain training regime is more the norm than the exception for natural language processing \cite{Dredze08online,Finkel09hierarchical}, and the design of multi-domain systems has been proposed for many language processing tasks. We focus here exclusively on MD machine translation, keeping in mind that similar problems and solutions (parameter sharing, instance selection / weighting, adversarial training, etc) have been studied in other contexts.

@@

Multi-domain translation was already proposed for statistical MT (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}).\fyTodo{Add also topic models refs} Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain labels give rise to additional features.

This latter strategy has also been widely used in NMT: the authors of \cite{Kobus17domaincontrol} inject an additional domain feature in their seq2seq model, either in the form of an extra (initial) domain-token or in the form of additional domain-feature associated to each word. These results are reproduced in \cite{Tars18multidomain}, which also considers, as we do, automatically induced domain tags. This technique also helps control the style of MT outputs in \cite{Sennrich16politeness,Niu18multitask}, and to encode the source or target languages in multilingual MT \cite{Firat16multiway,Johnson17google}. Domain control can also be performed on the target side, as in \cite{Chen16guided}, where a vector of topic describing the current document is included as an extra context in the softmax layer of the decoder. Such ideas are further developed in \cite{Chu18multilingual,Pham19generic}, where domain differences and commonalties are encoded in the network architecture: some parameters
are shared across all domains, while others are domain-specific. % (part of the embeddings in \cite{Pham19generic}).
